My title

### 2024-03-08 paper/paper.qmd
ran model

library(tidyverse)
library(palmerpenguins)
library(here)
```

@@

library(rstanarm)

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

# modelsummary::modelsummary(
#   list(
#     "First model" = first_model
#   ),
#   statistic = "mad",
#   fmt = 2
# )
```

>>>>

library(tidyverse)
library(palmerpenguins)
library(here)
library(rstanarm)
library(modelsummary)

```

@@

library(rstanarm)
political_preferences <-
  readRDS(file = here::here("models/political_preferences.rds"))

@@

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false
install.packages("modelsummary")

# Load the modelsummary package
library(modelsummary)

modelsummary(
  list(
    "Support Biden" = political_preferences
  ),
  statistic = "mad"
  )

```
